%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.0 (4/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Sagun} % Your first name
\familyname{Khatri} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{12800 Harrisglenn Drive Apt \#1534}{Austin, Texas 78753}
\mobile{(512) 853 0764}
\phone{(512) 524 2722}
% \fax{(000) 111 1113}
\email{sakh1979@gmail.com}
% \homepage{www.johnsmith.com}
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
\section{Objective}
\cvline{}
{I would like to use my skills to work with a team to solve the challenges presented
to us. I strive to learn and grow my skill set on the job and to further innovate 
on what I work on.}


%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
  \cvlistitem{Seven years of software engineering experience in application development 
              using Java (JSP, Servlets, EJB, Spring, Hibernate, JPA), and  
              application servers including WebLogic, Tomcat 5 -- 7, and JBoss 4 -- 6.}
  \cvlistitem{Broad knowledge of software engineering concepts, technologies, 
              methodologies, and practices. Experienced in designing and 
              implementing database schema, writing SQL queries in Oracle 9i -- 11g, 
              MySQL, and MS-SQL.}
  \cvlistitem{Designed and implemented financial software system to handle 
              Child Payments for the state of Illinois, Florida, Ohio, 
              California, Wisconsin and New Jersey.}


%----------------------------------------------------------------------------------------
%	PUBLICATION
%----------------------------------------------------------------------------------------
\section{Publication}
   \cvline{2012}{Khatri, Sagun, 
   \textsc{\textbf{SCTP Performance Improvement Based On Adaptive Retransmission Time-Out Adjustment}}, 
   Lambert Academic Publishing, ISBN 978-3846587089}


% --------------------------------------------------------------------------
% Technical Skills
% --------------------------------------------------------------------------
\section{Technical Skills}
  \cvline{Languages}{Java, HTML, JavaScript, XML, CSS, C, C++ Python, Scala}
  \cvline{Database}{Oracle, MS-SQL, MySQL}
  \cvline{Technologies}{JEE Technologies, AJAX, JSP, Servlet, EJB, Java, Structs, Hibernate, Spring, JPA}
  \cvline{OS Platforms}{Linux, Mac OS X (Tiger -- Mountain Lion), UNIX, Windows 95 -- Windows 7}
  \cvline{App. Servers}{JBoss, Apache Tomcat, WebLogic}
  \cvline{Version Ctrl}{Git, Perforce, PVCS}
  \cvline{Typesetting}{\LaTeX}
  \cvline{Application}{Adobe Photoshop, Adobe Dreamweaver, OmniGraffle, OmniGraphSketcher, Beyond Compare, Eclipse IDE.}
  \cvline{Shells}{Bash}
  \cvline{CI Tool}{Hudson}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

  \subsection{Professional Experience}
     \cventry{2008--Present}{Senior Java Developer}{\textsc{Xerox}}{Austin, TX}{}
     {\begin{itemize}
         \item Became a team lead of a rebuilding development team with my domain knowledge of the product.
         \item Responsibilities -- implementing client requirements, bug fixes, design, time line estimation, managing off shore team, and project planning.
         \item Involved in all phases of development lifecycle: Requirements, Design, Documentation, Implementation, Deployment, and Maintenance.
         \item Our product is a Java based web application that utilizes Structs 1.1, Spring Framework, JBoss AS, with Oracle 10g/11g as a backend.
     \end{itemize}}
     
     \cventry{2006--2007}{Mid Level Java Developer}{\textsc{Texas Department of Family and Protective Services}}{Austin, TX}{}
     {\begin{itemize}
         \item Worked on enhancing a web based application called IMPACT for processing child abuse cases.
         \item Used GRNDS framework for managing the control flow of the application.
         \item Developed Tuxedo Services in C to perform database operations.
         \item Configured WebLogic to connect to the Tuxedo services.
         \item Used Oracle 9i database as the back end.
         \item Used PVCS as the source control repository and Eclipse as the IDE.
     \end{itemize}}

  \subsection{Internship}
     \cventry{2005--2006}{Intern}{\textsc{I.B.M.}}{Rochester, MN}{}
     {\begin{itemize}
         \item Worked as an entry level developer in maintaining C code and SQL for the AS-400 Servers.
         \item Developed a database driven application using C and SQL.
         \item Used PVCS as the source control repository and JEdit as the editor.
     \end{itemize}}
  
  \subsection{Miscellaneous}
     \cventry{2001--2004}{Website Developer}{\textsc{Arts and Gallery Department of Luther College}}
     {Decorah, IA}{}
     {\begin{itemize}
         \item Designed webpage using Dreamweaver and Photoshop for the Art Department.
     \end{itemize}}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
   \cventry{2008--2011}{Masters of Computer Science}{Texas State University}{San 
               Marcos}{Texas}{}  % Arguments not required can be left empty
   \cventry{2001--2006}{Bachelor of Computer Science}{Luther College}{Decorah}{Iowa}{}
   \cventry{1999--2000}{Certificate in Web Centric Curriculum}{NIIT}{Kathmandu}{Nepal}{}
   \cventry{1997--1998}{Diploma in Information and System Management}{Aptech Computer Education}{Kathmandu}{Nepal}{}


%----------------------------------------------------------------------------------------

\end{document}
