%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.0 (4/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

% Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, 
% legalpaper, executivepaper or landscape; font families: sans or roman
\documentclass[11pt,letterpaper,sans]{moderncv}

% CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 
% 'banking'
\moderncvstyle{classic}

% CV color - options include: 'blue' (default), 'orange', 'green', 'red', 
% 'purple', 'grey' and 'black'
\moderncvcolor{black} 

% Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{lipsum} 

% Reduce document margins
\usepackage[scale=0.75]{geometry}

% Uncomment to change the width of the dates column
%\setlength{\hintscolumnwidth}{3cm} 

% For the 'classic' style, uncomment to adjust the width of the space allocated 
% to your name
%\setlength{\makecvtitlenamewidth}{10cm}

%------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%------------------------------------------------------------------------------

\firstname{Sagun} % Your first name
\familyname{Khatri} % Your last name

% All information in this block is optional, comment out any 
% lines you don't need
\title{Principal Developer}
\address{12800 Harrisglenn Drive}{Austin, Texas 78753}
% \mobile{(512) 853 0764}
\phone{(512) 853 0764}
% \fax{(000) 111 1113}
\email{sakh1979@gmail.com}
% \homepage{www.johnsmith.com}
% \extrainfo{additional information}

% The first bracket is the picture height, the second is the thickness of the 
% frame around the picture (0pt for no frame)
% \photo[70pt][0.4pt]{pictures/picture} 
% \quote{"A witty and playful quotation" - John Smith}

%------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%------------------------------------------------------------------------------
%	OBJECTIVE
%------------------------------------------------------------------------------
%% \section{Objective}
%% \cvline{}
%% {I would like to use my skills to work with a team to solve the challenges 
%% presented to us. I strive to learn and grow my skill set on the job and to 
%% further innovate on what I work on.}


%------------------------------------------------------------------------------
%	SUMMARY
%------------------------------------------------------------------------------
\section{Summary}
  \cvlistitem{8+ years of professional software engineering experience,
              delivering consumer-facing web applications with a service
              oriented architecture.}
  \cvlistitem{Proven track record of delivering products on time with
              minimal oversight.}
  \cvlistitem{Expertise in Java based (highly scalable, distributed,
              and tiered) web applications.}
  \cvlistitem{Broad knowledge of software engineering concepts, 
              methodologies, and practices.}
  \cvlistitem{Proficient in Linux/UNIX environments, shell scripting, Java 
              Enterprise developments, Relational Database Management
              Systems, and software deployments. Extensive knowledge and
              proficiency in open source softwares such as Spring, REST,
              Hibernate, JUnit, Git, Maven, Ant, and Hudson CI.}
  \cvlistitem{Designed, implemented, and documented JEE applications for
              large-scale mission critical enterprise systems, with high
              volume transaction processing features.}


%------------------------------------------------------------------------------
%	PUBLICATION
%------------------------------------------------------------------------------
\section{Publication}
   \cvline{2012}{Khatri, Sagun, 
   \textsc{\textbf{SCTP Performance Improvement Based On Adaptive 
   Retransmission Time-Out Adjustment}}, 
   Lambert Academic Publishing, ISBN 978-3846587089}


% --------------------------------------------------------------------------
% Technical Skills
% --------------------------------------------------------------------------
\section{Technical Skills}
  \cvline{Languages}
         {Java, Shell Scripts, PL/SQL, HTML, JavaScript, XML, JSON, CSS, 
         C, Python}
  \cvline{Database}
         {Oracle, MS-SQL, MySQL}
  \cvline{Technologies}
         {REST WS, Hibernate, Spring, JPA, AJAX, JSP, Servlet, Structs, 
         MQ Messaging}
  \cvline{OS Platforms}
         {Linux, Mac OS X (Tiger--Mavericks), UNIX, Windows 95--Windows 7}
  \cvline{App. Servers}
         {JBoss, Apache Tomcat, WebLogic}
  \cvline{Version Ctrl.}
         {Git, Perforce, PVCS}
  \cvline{Build Tool}
         {Ant, Maven, Make}
  \cvline{Typesetting}
         {\LaTeX}
  \cvline{Tools}
         {Emacs, JIRA, Stash, SQL Developer, SQL*Loader, Eclipse, Bugzilla}
  \cvline{CI Tool}
         {Bamboo, Hudson}


%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------------

\section{Experience}

  \subsection{Professional Experience}
     \cventry{2013--Present}{Principal Developer}
     {\textsc{Xerox}}{Austin, TX}{}
     {\begin{itemize}
         \item Provided technical leadership on projects, mentored junior 
               developers, participated in highly technical enterprise 
               systems design and implementation.
         \item Designed, implemented, and documented system level and 
               application level JEE application environments and frameworks 
               for large-scale mission critical enterprise systems.
         \item Designed and lead the implementation of configuration 
               management systems, including build and deployment procedures 
               and tools, automation and process control support system.
         \item Transformed complex requirements into working, maintainable 
               enterprise-level solutions.
         \item Provided necessary support to other team members as required 
               to help deliver systems on schedule and with high quality.
     \end{itemize}}
      
     \cventry{2008--2012}{Senior Developer}
     {\textsc{Xerox}}{Austin, TX}{}
     {\begin{itemize}
         \item Involved in all phases of development lifecycle: 
               Requirements, Design, Documentation, Implementation, 
               Deployment, and Maintenance.
         \item Responsibilities included implementing client requirements, bug
               fixes, design, time line estimation, managing and training off
               shore team, and project planning.
         \item Our product is a Java based web application that utilizes 
               Structs 1.1, Spring Framework, JBoss AS, with Oracle 10g/11g 
               as a backend.
     \end{itemize}}
     
     \cventry{2006--2007}{Developer}
     {\textsc{Texas Department of Family and Protective Services}}
             {Austin, TX}{}
     {\begin{itemize}
         \item Enhanced web based application (IMPACT) for processing child 
               abuse cases.
         \item Used GRNDS (Accenture's framework) for managing the control flow 
               of the application.
         \item Developed Tuxedo Services in C to perform database operations.
         \item Configured WebLogic to connect to the Tuxedo services.
         \item Used Oracle 9i database as the back end.
     \end{itemize}}

  \subsection{Internship}
     \cventry{2005--2006}{Intern}{\textsc{I.B.M.}}{Rochester, MN}{}
     {\begin{itemize}
         \item Maintained legacy code written in C for AS-400 system.
         \item Developed database driven application using C and SQL.
     \end{itemize}}
  
  \subsection{Miscellaneous}
     \cventry{2001--2004}{Website Developer}
     {\textsc{Arts and Gallery Department of Luther College}}
     {Decorah, IA}{}
     {\begin{itemize}
         \item Designed static webpage using Dreamweaver and Photoshop
               for the Art Department.
     \end{itemize}}


%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

\section{Education}
   % Arguments not required can be left empty
   \cventry{2008--2011}{Masters of Computer Science}
           {Texas State University}{San Marcos}{Texas}{}
   \cventry{2001--2006}{Bachelor of Computer Science}
           {Luther College}{Decorah}{Iowa}{}
   \cventry{1999--2000}{Certificate in Web Centric Curriculum}{NIIT}
           {Kathmandu}{Nepal}{}
   \cventry{1997--1998}{Diploma in Information and System Management}
           {Aptech Computer Education}{Kathmandu}{Nepal}{}


%------------------------------------------------------------------------------

\end{document}
